A holomorphic approach to membranes and fivebranes

### 2022-06-13 fivebranes/fact.tex
weights

\begin{prop}
\end{prop}

For each $n \in \ZZ$ and open set $U \subset \C^3$, let 
\[
\pi_* \cL_{sugra}(U)^{(n)} \subset \cL_{sugra}(\pi^{-1} U)
\]
be the weight $n$ eigenspace with respect to this $\C^\times$ action. 
The $\C^\times$ action is compatible with the $\Z/2$ graded $L_\infty$ structure on $\cL_{sugra}$. 
Since the $n$th eigenspace is trivial when $n < -1$, we see that the product
\[
(\Bar{\pi}_* \cL_{sugra})(U) \define \prod_{n \geq -1} (\pi_*\cL_{sugra})(U)^{(n)}
\]
is equipped with the structure of a $\Z/2$ graded $L_\infty$ algebra.
In this way, the assignment 
\[
\Bar{\pi}_* \cL_{sugra} \colon U \mapsto (\Bar{\pi}_* \cL_{sugra})(U) 
\]
defines a sheaf of $\Z/2$ graded $L_\infty$ algebras on $\C^3$.

>>>>

\begin{prop}
The $L_\infty$ structure on $\cL_{sugra}$ equivariant for this $\C^\times$ action. 
The odd symplectic form on $\cL_{sugra}$ is weight $-1$ for this $\C^\times$ action. 
\end{prop}
\begin{proof}
The only nontrivial bracket to check compatibility with the $\C^\times$ action is the one which takes two $\gamma$-type sections to a $\mu$-type section of the form
\[
[\gamma_1, \gamma_2] = \Omega^{-1} \vee (\del \gamma_1 \wedge \del \gamma_2) 
\]
where $\Omega \vee (-)$ is the operation which takes a four-form

It suffices to check equivariance in local coordinates; there are three cases.
Suppose $\gamma_1(t;w,z) = f^i(t;w,z) \d z_i$ and $\gamma_2(t;w,z) = g^j(t;w,z) \d z_j$where $f^i,g^j$ are de Rham--Dolbeault forms for $i,j=1,2,3$. 
Then $\lambda \cdot \gamma_1 = \lambda^{-1} f^i(\lambda t;\lambda w, z) \d z_i$ and $\lambda \cdot \gamma_2 = \lambda^{-1} g^j(\lambda t;\lambda w, z) \d z_j$. 
Thus, if the $\mu$-type field is expanded as $[\gamma_1,\gamma_2] = F^k(t;w,z) \del_{z_k} + G^a (t;w,z) \del_{w_a}$ for some de Rham--Dolbeault forms $F^k,G^a$, $k=1,2,3,a=1,2$, it suffices to show that 
\beqn
\begin{array}{llll}
\label{eqn:lambda1} \lambda \cdot \left(F^k(t;w,z) \del_{z_k} \right) & = \lambda^{-2} F^k(\lambda t;\lambda w,z) \del_{z_k} \\
\lambda \cdot \left(G^a(t;w,z) \del_{w_a} \right) & = \lambda^{-2} G^a(\lambda t;\lambda w,z) \del_{w_a} .
\end{array}
\eeqn
We expand $\del \gamma_1 \wedge \del \gamma_2$ to three terms
\begin{multline}
\del_{w_a} f^i(t;w,z) \del_{z_l} g^j(t;w,z) \d w_a \d z_i \d z_l \d z_j + \del_{z_k} f^i(t;w,z) \del_{w_b} g^j(t;w,z) \d z_k \d z_i \d w_b \d z_j \\  + \del_{w_a} f^i(t;w,z) \del_{w_b} g^j(t;w,z) \d w_a \d z_i \d w_b \d z_j .
\end{multline}
Thus in the notation above we have 
\begin{align*}
F^k (t;w,z) & = \ep_{ab} \ep_{ijk} \del_{w_a} f^i(t;w,z) \del_{w_b} g^j(t;w,z) \\
G^a(t;w,z) & = \ep_{ilj} \ep_{ab} \del_{w_a} f^i(t;w,z) \del_{z_l} g^j(t;w,z)
+ \ep_{kij} \ep_{ab} \del_{z_k} f^i(t;w,z) \del_{w_a} g^j(t;w,z)  .
\end{align*}
We compute the action of $\lambda \in \C^\times$ on $\mu = F^k \del_{z_k}$
\[
\lambda \cdot \left(F^k \del_{z_k} \right) = \ep_{ab} \ep_{ijk} \lambda^{-1} \del_{w_a} f^i(\lambda t;\lambda w,z) \lambda^{-1} \del_{w_b} g^j(\lambda t;\lambda w,z) \del_{z_k} .
\]
Thus the first part of \eqref{eqn:lambda1} is satisfied. 
Similarly we observe that $\lambda \cdot \left(G^a(t;w,z) \del_{w_a} \right)  = \lambda^{-2} G^a(\lambda t;\lambda w,z) \del_{w_a}$.

The next case is when $\gamma_1(t;w,z) = f^i(t;w,z) \d z_i$ and $\gamma_2(t;w,z) = g^a(t;w,z) \d w_a$where $f^i,g^a$ are de Rham--Dolbeault forms for $i=1,2,3$ and $a=1,2$. 
Then $\lambda \cdot \gamma_1 = \lambda^{-1} f^i(\lambda t;\lambda w, z) \d z_i$ and $\lambda \cdot \gamma_2 = g^a(\lambda t;\lambda w, z) \d w_a$. 
Thus, if the $\mu$-type field is expanded as $[\gamma_1,\gamma_2] = F^k(t;w,z) \del_{z_k} + G^a (t;w,z) \del_{w_a}$ for some de Rham--Dolbeault forms $F^k,G^a$, $k=1,2,3,a=1,2$, it suffices to show that 
\beqn
\begin{array}{llll}
\label{eqn:lambda2} \lambda \cdot \left(F^k(t;w,z) \del_{z_k} \right) & = \lambda^{-1} F^k(\lambda t;\lambda w,z) \del_{z_k} \\
\lambda \cdot \left(G^a(t;w,z) \del_{w_a} \right) & = \lambda^{-1} G^a(\lambda t;\lambda w,z) \del_{w_a} .
\end{array}
\eeqn
We expand $\del \gamma_1 \wedge \del \gamma_2$ to three terms
\begin{multline}
\del_{w_b} f^i(t;w,z) \del_{z_j} g^a(t;w,z) \d w_b \d z_i \d z_j \d w_a + \del_{z_k} f^i(t;w,z) \del_{w_b} g^a(t;w,z) \d z_k \d z_i \d w_b \d w_a \\  + \del_{z_j} f^i(t;w,z) \del_{z_k} g^a(t;w,z) \d z_j \d z_i \d z_k \d w_a .
\end{multline}
Thus in the notation above we have 
\begin{align*}
F^k (t;w,z) & = \ep_{ab} \ep_{ijk} \del_{w_a} f^i(t;w,z) \del_{z_l} g^b(t;w,z) + \ep_{ab} \ep_{kij} \del_{z_k} f^i(t;w,z) \del_{w_a} g^b(t;w,z) \\
G^a(t;w,z) & = \ep_{ab} \ep_{jik} \del_{z_j} f^i(t;w,z) \del_{z_k} g^b(t;w,z) .
\end{align*}
We compute the action of $\lambda \in \C^\times$ on $\mu = G^a \del_{z_a}$
\[
\lambda \cdot \left(G^a \del_{w_a} \right) = \ep_{ab} \ep_{jik} \del_{z_j} f^i(t;w,z) \del_{z_k} g^b(t;w,z) \lambda^{-1} \del_{w_a} .
\]
Thus the second part of \eqref{eqn:lambda2} is satisfied. 
Similarly we observe that $\lambda \cdot \left(F^k(t;w,z) \del_{z_k} \right)  = \lambda^{-2} F^k(\lambda t;\lambda w,z) \del_{z_k}$.

The last case is when $\gamma_1(t;w,z) = f^a(t;w,z) \d w_a$ and $\gamma_2(t;w,z) = g^b(t;w,z) \d w_b$where $f^a,g^b$ are de Rham--Dolbeault forms for and $a,b=1,2$.
The argument is nearly identical so we omit the details.

\end{proof}

For each $n \in \ZZ$ and open set $U \subset Z$, let 
\[
\pi_* \cL_{sugra}(U)^{(n)} \subset \cL_{sugra}(\pi^{-1} U)
\]
be the weight $n$ eigenspace with respect to this $\C^\times$ action. 
%The $\C^\times$ action is compatible with the $\Z/2$ graded $L_\infty$ structure on $\cL_{sugra}$. 
Since the $n$th eigenspace is trivial when $n < -1$, we see that the product
\[
(\Bar{\pi}_* \cL_{sugra})(U) \define \prod_{n \geq -1} (\pi_*\cL_{sugra})(U)^{(n)}
\]
is equipped with the structure of a $\Z/2$ graded $L_\infty$ algebra.
In this way, the assignment 
\[
\Bar{\pi}_* \cL_{sugra} \colon U \mapsto (\Bar{\pi}_* \cL_{sugra})(U) 
\]
defines a sheaf of $\Z/2$ graded $L_\infty$ algebras on $\C^3$.
